The extended light profiles of the Sculptor and Ursa Minor dwarf galaxies: Innate nature or tidal nurture?

### 2025-11-13 thesis/acknowledgements.tex
paper updates

To Raphaël, who has helped inspire and direct this project. To everyone
who has helped provide me opportunities to share work, and share
wonderful ideas with me. Isabel, Jens, Eduardo, Jorge, David, Justin,
Eugene, Azi, José, and many others.

To Jax, who has been a support along the way, guiding my research
methods and project.

To all of my new friends I have made along the way. Ruxin, Aviv. To
Pranav, Ted, Jono, Adrianne, Praneet, Will, Maeve, Ewoud, Anne, Anya,
Shoshanah. To Akshara and Simon for all your personal and professional
advice. We have built a wonderful community of students in this
department. To all the students who have since moved on and show what we
may be: Bobby, Leo, Ryan, Katie, Fletcher, Ayden, Maheyer, Jess, Dhwani,
Spencer, Mallory, Omar, Isaac, and Dasha.

And to my friends across UVic, Wyatt, Rosemary, Maggie. To the
Linguistics extended family and team \emph{adequate}. Melody, Lily,
Gillian, Stephen, Jamie, Chloë, Alyssa, Kyle, and Marcus. You are all
wonderful human beings, cooks, and always a joy to spend time with.

To my musical friends, Adrienne, Alex for our shared joy in music
making. And Steve, for showing me the joy in a simple life and beautiful
music.

@@

To my fellow fibre friends and crafters. Leise, Wes, Ashley, Sabrina,
Sarah. To the graduate student society for continuing to connect us
across departments.

To the international community, and my international friends---Marcela,
Bernardo, Daniel, Victor, Walla, Mehrab, and everyone else I have met.

@@

To my long-time friends. Nikola and Eric. Mikey and Anthony. Anya, Kaia,
Alyssa, Aahliyah, Cameron. May we continue to find each other even as we
drift apart.

To my parents for their continuous support throughout this project. To
my grandparents for always being there.

To Nolan and Olivia, always a joy to see each other. To Bridget and
Gretchen. To my extended family. And to my siblings for always being a
source of joy.

>>>>

To Raphaël, who has helped inspire and direct this project, and to
everyone who has shared ideas and opportunities along the way: Isabel,
Jens, Eduardo, Jorge, David, Justin, Eugene, Azi, José, and many others.

To Jax for you guidance and personal support for this project.

To all of my new friends I have made along the way---Ruxin, Aviv. To
Pranav, Ted, Jono, Adrianne, Praneet, Will, Maeve, Ewoud, Anne, Anya,
Shoshanah. To Akshara and Simon for all your personal and professional
advice. We have built a wonderful graduate community. To all the
students who have since moved on but still inspire me: Bobby, Leo, Ryan,
Katie, Fletcher, Ayden, Maheyer, Jess, Dhwani, Spencer, Mallory, Omar,
Isaac, and Dasha.

To my friends across UVic: Wyatt, Rosemary, Maggie. To the Linguistics
extended family and team \emph{adequate}: Melody, Lily, Gillian,
Stephen, Jamie, Chloë, Alyssa, Kyle, and Marcus. You are all wonderful
human beings, cooks, and always a joy to spend time with.

To my musical friends, Adrienne and Alex, for our shared joy in music
making. And Steve, for showing me the joy in a simple life and beautiful
music.

@@

To my fellow fibre friends and crafters: Leise, Wes, Ashley, Sabrina,
Sarah. To the graduate student society for continuing to connect us
across departments.

To the international community, and my international friends---Marcela,
Bernardo, Daniel, Victor, Mehrab, and many others.

@@

To my long-time friends---Nikola, Eric, Mikey, Anthony, Anya, Kaia,
Alyssa, Aahliyah, Cameron---may we continue to stay in touch.

To my parents for their continuous support throughout this project. To
my grandparents for always being there. To Nolan and Olivia, always a
joy to see each other. To Bridget and Gretchen. To my extended family.
And to my siblings for always being a source of joy.

### 2025-11-13 thesis/introduction.tex
paper updates

\begin{table*}[t]
\centering
\caption[Observed Properties of Sculptor]{Observed properties of Sculptor. References are: (1) Muñoz et al. (2018, Sérsic fit), (2) Tran et al. (2022, RR lyrae distance), (3) Alan W. McConnachie and Venn (2020b), (4) Arroyo-Polonio et al. (2024). }
\label{tbl:scl_obs_props}
\begin{tabular}{lll}
\toprule
parameter & value & Source\\
\midrule
$\alpha$ & $15.0183 \pm 0.0012^\circ$ & 1\\
$\delta$ & $-33.7186 \pm 0.0007^\circ$ & ”\\
distance modulus & $19.60 \pm 0.05$ & 2\\
distance & $83.2 \pm 2$ kpc & ”\\
$\mu_{\alpha*}$ & $0.099 \pm 0.002 \pm 0.017$ mas yr$^{-1}$ & 3\\
$\mu_\delta$ & $-0.160 \pm 0.002_{\rm stat} \pm 0.017_{\rm sys}$ mas yr$^{-1}$ & ”\\
LOS velocity & $111.2 \pm 0.3\ {\rm km\,s^{-1}}$ & 4\\
$\sigma_v$ & $9.7\pm0.2\ {\rm km\,s^{-1}}$ & ”\\
$R_h$ & $9.79 \pm 0.04$ arcmin & 1\\
ellipticity & $0.37 \pm 0.01$ & ”\\
position angle & $94\pm1^\circ$ & ”\\
$M_V$ & $-10.82\pm0.14$ & ”\\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\centering
\caption[Observed Properties of Ursa Minor]{Observed properties of Ursa Minor. References are: (1) Muñoz et al. (2018, Sérsic fit), (2) Garofalo et al. (2025, RR lyrae distance), (3) Alan W. McConnachie and Venn (2020a), (4) Pace et al. (2020), average of MMT and Keck results with systematic uncertainty from Appendix \ref{sec:extra_rv_models} discussion. }
\label{tbl:umi_obs_props}
\begin{tabular}{lll}
\toprule
parameter & value & Source\\
\midrule
$\alpha$ & $ 227.2420 \pm 0.0045$˚ & 1\\
$\delta$ & $67.2221 \pm 0.0016$˚ & ”\\
distance modulus & $19.23 \pm 0.11$ & 2\\
distance & $70.1 \pm 3.6$ kpc & ”\\
$\mu_\alpha*$ & $-0.124 \pm 0.004 \pm 0.017$ mas yr$^{-1}$ & 3\\
$\mu_\delta$ & $0.078 \pm 0.004_{\rm stat} \pm 0.017_{\rm sys}$ mas yr$^{-1}$ & ”\\
LOS velocity & $-245.9 \pm 0.3_{\rm stat} \pm 1_{\rm sys}$ km s$^{-1}$ & 4\\
$\sigma_v$ & $8.6 \pm 0.3$ & ”\\
$R_h$ & $11.62 \pm 0.1$ arcmin & 1\\
ellipticity & $0.55 \pm 0.01$ & ”\\
position angle & $50 \pm 1^\circ$ & ”\\
$M_V$ & $-9.03 \pm 0.05$ & ”\\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}[t]
\centering
\caption[Observed properties of Sculptor]{Observed properties of Sculptor. References are: (1) Muñoz et al. (2018, Sérsic fit), (2) Tran et al. (2022, RR lyrae distance), (3) Alan W. McConnachie and Venn (2020b), (4) Arroyo-Polonio et al. (2024). }
\label{tbl:scl_obs_props}
\begin{tabular}{lll}
\toprule
parameter & value & Source\\
\midrule
$\alpha$ & $15.0183 \pm 0.0012^\circ$ & 1\\
$\delta$ & $-33.7186 \pm 0.0007^\circ$ & ”\\
distance modulus & $19.60 \pm 0.05$ & 2\\
distance & $83.2 \pm 2$ kpc & ”\\
$\mu_{\alpha*}$ & $0.099 \pm 0.002 \pm 0.017$ mas yr$^{-1}$ & 3\\
$\mu_\delta$ & $-0.160 \pm 0.002_{\rm stat} \pm 0.017_{\rm sys}$ mas yr$^{-1}$ & ”\\
LOS velocity & $111.2 \pm 0.3\ {\rm km\,s^{-1}}$ & 4\\
$\sigma_v$ & $9.7\pm0.2\ {\rm km\,s^{-1}}$ & ”\\
$R_h$ & $9.79 \pm 0.04$ arcmin & 1\\
ellipticity & $0.37 \pm 0.01$ & ”\\
position angle & $94\pm1^\circ$ & ”\\
$M_V$ & $-10.82\pm0.14$ & ”\\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\centering
\caption[Observed properties of Ursa Minor]{Observed properties of Ursa Minor. References are: (1) Muñoz et al. (2018, Sérsic fit), (2) Garofalo et al. (2025, RR lyrae distance), (3) Alan W. McConnachie and Venn (2020a), (4) Pace et al. (2020), average of MMT and Keck results with systematic uncertainty from Appendix \ref{sec:extra_rv_models} discussion. }
\label{tbl:umi_obs_props}
\begin{tabular}{lll}
\toprule
parameter & value & Source\\
\midrule
$\alpha$ & $ 227.2420 \pm 0.0045$˚ & 1\\
$\delta$ & $67.2221 \pm 0.0016$˚ & ”\\
distance modulus & $19.23 \pm 0.11$ & 2\\
distance & $70.1 \pm 3.6$ kpc & ”\\
$\mu_\alpha*$ & $-0.124 \pm 0.004 \pm 0.017$ mas yr$^{-1}$ & 3\\
$\mu_\delta$ & $0.078 \pm 0.004_{\rm stat} \pm 0.017_{\rm sys}$ mas yr$^{-1}$ & ”\\
LOS velocity & $-245.9 \pm 0.3_{\rm stat} \pm 1_{\rm sys}$ km s$^{-1}$ & 4\\
$\sigma_v$ & $8.6 \pm 0.3$ & ”\\
$R_h$ & $11.62 \pm 0.1$ arcmin & 1\\
ellipticity & $0.55 \pm 0.01$ & ”\\
position angle & $50 \pm 1^\circ$ & ”\\
$M_V$ & $-9.03 \pm 0.05$ & ”\\
\bottomrule
\end{tabular}
\end{table*}
